A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-03-15 writeup/paper.tex
equations

In order to address the quality of the translations we received on the dictionary task, we constructed a pipeline in which the output of the translation HIT was reviewed by humans in a second evaluation HIT, described above.  We quantified the quality of each translation assignment based on the output of the evaluation HIT as follows: \\
\textbf{In English, so people know what we did:}
\begin{align}	
	Quality = \frac{\# \text{correct controls}}{\# \text{controls}}
\end{align}	
where a control is correct if it matches or is judged to be synonymous with the gold standard translation during the second pass HIT. \\
\textbf{Mathified, to give the impression of rigor and intellect:}
\begin{align}	
	Quality(assign_i) = \frac{1}{k}\sum\limits_{j=1}^{k_i}\mathbf{1}(t_{ij} \in Syns(a_j))
\end{align}	
where $k_i$ is the number of controls in the assignment $i$, $t_j$ is the Turker's provided translation of control word $j$ in assignment $i$, $a_j$ is the gold standard translation of control word $j$, $Syns(a_j)$ is the set of words judged to be synonymous with $a_j$ during the second pass HIT, and $\mathbf{1}(x)$ is 1 when $x$ is true.

@@

>>>>

In order to address the quality of the translations we received on the dictionary task, we constructed a pipeline in which the output of the translation HIT was reviewed by humans in a second evaluation HIT, described above.  We quantified the quality of each translation assignment based on the output of the evaluation HIT as follows: \\
\textbf{Version 1: In English, so people know what we did:}
\begin{align}	
	Quality = \frac{\# \text{correct controls}}{\# \text{controls}}
\end{align}	
where a control is correct if it matches or is judged to be synonymous with the gold standard translation during the second pass HIT. \\
\textbf{Version 2 : Mathified, to give the impression of rigor and intellect:}
\begin{align}	
	Quality(assign_i) = \frac{1}{k}\sum\limits_{j=1}^{k_i}\mathbf{1}(t_{ij} \in Syns(a_j))
\end{align}	
where $k_i$ is the number of controls in the assignment $i$, $t_j$ is the Turker's provided translation of control word $j$ in assignment $i$, $a_j$ is the gold standard translation of control word $j$, $Syns(a_j)$ is the set of words judged to be synonymous with $a_j$ during the second pass HIT, and $\mathbf{1}(x)$ is 1 when $x$ is true.

@@

Quality for a language is then given by
\begin{align}	
	Quality(lang_i) = \frac{\sum_{t_j \in Turkers(i)}Quality(t_j)}{\mid Turkers(i) \mid}
\end{align}	
where $Turkers(i)$ is the set of turkers who completed assignments for language $i$, and $Quality(t)$ is as above.
